---
title: "purchase_intention"
output: github_document
date: '2022-05-30'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

## Importing Libraries

```{r, warning=FALSE}
library("data.table")
library("caret")
library(lattice)
library("GGally")
library(ggplot2)
library(corrplot)
library(rattle)
library("gbm")

```

## Importing data file

```{r}
data = fread("online_shoppers_intention.csv")
```

##check dataset description and summary

```{r}
str(data)
head(data)
summary(data)
```

## check for missing values

```{r}
sum(is.na((data)))
```

##changing column type of logical into int then as factor

```{r}
data$Revenue <- ifelse(data$Revenue ==TRUE,1,0)
data$Revenue = as.factor(data$Revenue)
data$Weekend <- ifelse(data$Weekend ==TRUE,1,0)
data$Weekend = as.factor(data$Weekend)
```

##Performed encoding of variables by changing categorical variables into factors

```{r}
data$Browser = as.factor(data$Browser)
data$OperatingSystems  = as.factor(data$OperatingSystems)
data$Region  = as.factor(data$Region)
data$TrafficType = as.factor(data$TrafficType)
data$VisitorType = as.factor(data$VisitorType)
```

# Exploratory Data Analysis

##plotting the correlation graph to check correlation between different features

```{r}
correlation <- cor(data[,c(1:10)]) 
corrplot(correlation, method = "shade", type = "lower",diag = FALSE)
```

## plotting relation between Bounce rate and exit rate

```{r}
ggplot(data = data,aes(x = BounceRates, y = ExitRates))+ 
  geom_point(mapping = aes(color = Revenue)) + 
  geom_smooth(se = TRUE, alpha = 0.5,color="blue",method="lm")+theme()
```

## bar graphs for Revenue

```{r}
ggplot(data, aes(x = Revenue,fill=Revenue))+geom_bar()
```

## bar graphs Revenue vs Visitor Type

```{r}
ggplot(data, aes(x =VisitorType,fill=Revenue))+geom_bar()
```

## bar graphs for TrafficType

```{r}
ggplot(data, aes(x = TrafficType,fill=Revenue))+geom_bar()
```

## bar graphs for Region

```{r}
ggplot(data, aes(x = Region,fill=Revenue))+geom_bar(fill=rainbow(9))
```

## bar graphs for Special Day

```{r}
ggplot(data, aes(x = SpecialDay,fill=Revenue))+geom_bar(fill=rainbow(6))
```

## violin plot

```{r}
ggplot(data, aes(x = ProductRelated,y=Revenue))+geom_violin(trim = FALSE)
```

# Model Implementation

# set seed

```{r}
set.seed(12345678)
```

##splitting the data into training and testing set

```{r}
training = createDataPartition(y = data$Revenue, p = 0.75, list = FALSE)
train_set = data[training, ]
test_set = data[-training, ]
```
